---
title: "course5Project1"
author: "ChanterJohnDavid"
date: "11/1/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Repo

    Valid GitHub URL
    At least one commit beyond the original fork
    Valid SHA-1
    SHA-1 corresponds to a specific commit

Commit containing full submission

    Code for reading in the dataset and/or processing the data
    Histogram of the total number of steps taken each day
    Mean and median number of steps taken each day
    Time series plot of the average number of steps taken
    The 5-minute interval that, on average, contains the maximum number of steps
    Code to describe and show a strategy for imputing missing data
    Histogram of the total number of steps taken each day after missing values are imputed
    Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
    All of the R code needed to reproduce the results (numbers, plots, etc.) in the report
    
    
```{r}
library("dplyr")
library("ggplot2")
library("mlbench")
library("caret")
library("chron")



activityDF <- read.csv(file="/Users/douglasashworth/Documents/Coursera/DataScience/Course5/activity.csv", stringsAsFactors = FALSE)

 activityDF$steps[is.na(activityDF$steps)] <- 0

summary(activityDF)
str(activityDF)
names(activityDF)

print(head(activityDF))
print(summary(activityDF))
print(str(activityDF))

 hist(activityDF$steps, col='grey')
 
 avStepsPerDay <- c()
 medianStepsPerDay <- c()
 maxStepsIntervalPerDay <- c()
 maxStepPerDay <- c()
 maxInterval <- c()
 dailySteps <- c()
 totalNumStepsPerDay <- c()
 
 cntr <- 1
 maxCnt <- 2400/5
 print(maxCnt)
 fiveMinCntr <- 0
 #print(nrow(activityDF))
 print(activityDF$steps[0])
 dayCntr <- 0
 weekDayStepsAry <- c()
 weekendStepsAry <- c()
 
while (cntr <= nrow(activityDF)){
  
   fiveMinCntr <- 0
   tmpStepSum <- 0.0
   tmpCntr <- 0
   maxStep <- 0
   tmpSteps <- 0
   tmpStepAry <- c()
   currentDate <- activityDF$date[cntr]
   
   if (!is.weekend(currentDate)){
     wkdayFlag <- 1
     wkendFlag <- 0
   }else{
     wkendFlag <- 1
     wkdayFlag <- 0
   }
   
   while (fiveMinCntr <= 2355){
     
     tmpSteps <-  as.numeric(activityDF$steps[cntr])
     tmpStepAry <- c(tmpStepAry,tmpSteps)
     
     cntr <- cntr + 1
     fiveMinCntr <- fiveMinCntr + 5
     
   }
   meanSteps <- mean(tmpStepAry)
   medianSteps <- median(tmpStepAry)
   maxSteps <- max(tmpStepAry)
   maxInterval <- which.max(tmpStepAry)*5
   totalNumSteps <- sum(tmpStepAry)
   
   avStepsPerDay <- c(avStepsPerDay,meanSteps)
   medianStepsPerDay <- c(medianStepsPerDay,medianSteps) 
   maxStepPerDay <- c(maxStepPerDay,maxSteps)
   maxStepsIntervalPerDay <- c(maxStepsIntervalPerDay,maxInterval)
   totalNumStepsPerDay <- c(totalNumStepsPerDay,totalNumSteps)
   
   if (wkdayFlag == 1){
     weekDayStepsAry <- c(weekDayStepsAry,meanSteps)
   }else{
     weekendStepsAry <- c(weekendStepsAry,meanSteps)
   }
   
   dayCntr <- dayCntr + 1
    
}  

day <- 1:dayCntr 
qplot(day,totalNumStepsPerDay,geom = c("point","line"))
hist(totalNumStepsPerDay)
qplot(day,avStepsPerDay,geom = c("point","line"))
qplot(day,medianStepsPerDay,geom = c("point","line"))
qplot(day,maxStepPerDay,geom = c("point","line"))
qplot(day,maxStepsIntervalPerDay,geom = c("point","line"))
#print(mean(maxStepsIntervalPerDay))
#print(median(maxStepsIntervalPerDay))
wkday <- 1:length(weekDayStepsAry)
wkendDay <- 1:length(weekendStepsAry)
par(mfrow = c(1,2))
plot(wkday,weekDayStepsAry)
plot(wkendDay,weekendStepsAry)

par(mfrow = c(1,2))
boxplot(weekDayStepsAry, main="Average Weekday Steps")
boxplot(weekendStepsAry, main="Average Weekend Steps")
#plot(maxStepsIntervalPerDay)

```

## Including Plots

You can also embed plots, for example:

```{}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
